---
title: "Factor Analysis Table - Web-Widget"
author: "Ivan Voronin"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE, eval=FALSE}
rmarkdown::render('intro.Rmd',
                  output_file = '../docs/intro.html')
```

[ivan.a.voronin@gmail.com](mailto:ivan.a.voronin@gmail.com)

[https://github.com/IvanVoronin/FAT](https://github.com/IvanVoronin/FAT)

This package provides a web-widget for interactive presentation of results from
exploratory factor analysis. The function `loadings2table` accepts a matrix, a
data frame or an output from `fa` function (from the 
[`psych` package](https://cran.r-project.org/web/packages/psych/index.html)).

```{r eval=FALSE}
## Install the package
# install.packages('devtools')
library(devtools)
install_github('ivanvoronin/FAT')
```

```{r}
# Load packages
library(FAT)
library(psych)
```

```{r}
## This is the toy data from psych
## Details in ?bfi
data(bfi)
bfi <- bfi[, 1:25]

## The BFI items will appear in hint popover on click
hints <- c(
  A1 = "Am indifferent to the feelings of others. (q_146)",
  A2 = "Inquire about others' well-being. (q_1162)",
  A3 = "Know how to comfort others. (q_1206)",
  A4 = "Love children. (q_1364)",
  A5 = "Make people feel at ease. (q_1419)",
  C1 = "Am exacting in my work. (q_124)",
  C2 = "Continue until everything is perfect. (q_530)",
  C3 = "Do things according to a plan. (q_619)",
  C4 = "Do things in a half-way manner. (q_626)",
  C5 = "Waste my time. (q_1949)",
  E1 = "Don't talk a lot. (q_712)",
  E2 = "Find it difficult to approach others. (q_901)",
  E3 = "Know how to captivate people. (q_1205)",
  E4 = "Make friends easily. (q_1410)",
  E5 = "Take charge. (q_1768)",
  N1 = "Get angry easily. (q_952)",
  N2 = "Get irritated easily. (q_974)",
  N3 = "Have frequent mood swings. (q_1099)",
  N4 = "Often feel blue. (q_1479)",
  N5 = "Panic easily. (q_1505)",
  O1 = "Am full of ideas. (q_128)",
  O2 = "Avoid difficult reading material.(q_316)",
  O3 = "Carry the conversation to a higher level. (q_492)",
  O4 = "Spend time reflecting on things. (q_1738)",
  O5 = "Will not probe deeply into a subject. (q_1964)"
)
```

<div class="alert alert-info">
<h3 class="alert-heading" style="color:inherit">Responsive table</h4>
This is a table that presents factor loadings interactively to simplify the
exploration of factor analysis results.

- For a __default sorting order__, each item is assigned to a factor, the factor it
loads most. The loadings are sorted in ascending order within the factor they 
assigned to. __'Reorder'__ button applies the default sorting scheme.
- Alternatively, the table can be __sorted by a column__ by clicking on the header
of this column.
- 'Cutoff' field defines the threshold value to __filter the loadings__. The 
values below the threshold are excluded. Mind that the there may be a delay 
between the change of cutoff and the update of the table.
- 'Filter' field allows __filtering the items by their labels__.
- Click on a row to get a __hint with item's content__. 
Click again to close the hint. Double clink anywhere in the document closes all 
hints.
- Drag the index of a row to __rearrange items' order__.
- Use export buttons beneath the table to copy or __save as xlsx, csv or 
pdf__.
- `loadings2table` integrates with __`psych` package__ by extracting factor
loadings and explained variance from the return of `fa` function. Otherwise, the
loadings can be passed as matrix, refer to `?loadings2table`.
</div>

```{r message=FALSE}
## Factor analysis using psych
FA <- fa(bfi, nfactors = 5,
     n.iter = 100)

## Render the table
loadings2table(FA, 
               hints = hints)
```


